03_wrangle

### 2020-08-26 analysis/03_datawrangling.Rmd
now with removal venn

```{r setup}
library(tidyverse)
library(readr)

source("../R/themes.R")
```

@@

```{r allDEG}
DEG_path <- "../results/DEseq2/treatment/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

@@

>>>>

```{r setup}
library(tidyverse)
library(readr)
library(VennDiagram)

source("../R/themes.R")

knitr::opts_chunk$set(echo = TRUE, message = F, fig.path = '../figures/')
```

@@

```{r allDEG, results=F}
DEG_path <- "../results/DEseq2/treatment/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

@@

### overlapp

```{r}
removalcomps <- c("inc.d3_m.inc.d3", "inc.d9_m.inc.d9", "inc.d17_m.inc.d17", "hatch_m.n2")
early <- c("early_inc.d9", "hatch_early")
late <- c("hatch_prolong", "inc.d17_prolong")

filteredDEGs %>%
  filter(comparison %in% removalcomps)  %>%
  select(sex:gene) %>%
  pivot_wider(names_from = comparison, values_from = direction)

hatch_m.n2DEGs <- filteredDEGs %>%
  filter(comparison == "hatch_m.n2") %>%
  drop_na() %>%
  pull(gene)

inc.d17_m.inc.d17DEGs <- filteredDEGs %>%
  filter(comparison == "inc.d17_m.inc.d17") %>%
  drop_na() %>%
  pull(gene)

inc.d3_m.inc.d3DEGs <- filteredDEGs %>%
  filter(comparison == "inc.d3_m.inc.d3") %>%
  drop_na() %>%
  pull(gene)

inc.d9_m.inc.d9DEGs <- filteredDEGs %>%
  filter(comparison == "inc.d9_m.inc.d9") %>%
  drop_na() %>%
  pull(gene)

# Generate 3 sets of 200 words
# Chart

venn.diagram(
  x = list(hatch_m.n2DEGs, inc.d17_m.inc.d17DEGs, 
           inc.d3_m.inc.d3DEGs, inc.d9_m.inc.d9DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn.png',
  output=FALSE,
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "No. of genes that respond to offspring removal",
  sub = "9 shared genes: \nPHGDH, NRG2, LHX9, SSTR3, VTN, SARM1, ALK, LPAR1, and APOH" )

intersect(hatch_m.n2DEGs, inc.d17_m.inc.d17DEGs) %>%
  intersect(.,inc.d3_m.inc.d3DEGs) %>%
  intersect(.,inc.d9_m.inc.d9DEGs)
```
